---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# smokingPrevalence

<!-- badges: start -->
<!-- badges: end -->

The goal of smokingPrevalence is to store functions that are used in analysis for 
smoking prevalence including ONS public prevalence information to compare to.

## Installation

You can install the development version of smokingPrevalence from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Lextuga007/smokingPrevalence")
```

## ONS public smoking prevalence data

The data is released in wide form and the following imports this data as it appears
in the spreadsheet form:

```{r example}
library(smokingPrevalence)

get_ons_smoking()
```

To tidy the data, as in move it to long form and to clean the 2 row headers to 1:

```{r}
library(smokingPrevalence)
library(dplyr)
library(stringr) # cannot knit without - should be ok with dependency?

tidy_ons_smoking()
```

Reference: The function format of getting data and tidying data was introduced to 
the CDU Data Science Team by Milan Wiedemann who [blogged about it](https://cdu-data-science-team.github.io/team-blog/posts/2021-08-06-nottshcverse/)
